---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

# FromQuandl

The goal of FromQuandl is to easy the seach, download and data preprocessing that often happen when using the `Quandl` package in R.    

## Installation

You can install FromQuandl from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Reckziegel/FromQuandl")
```

## Example

Suppose you would like to download the Current Account Balance (as % of GDP) for all countries of a specific region or with a similar economic characteristic, like the G7, for example. Use the `imf_search()` function to discover the Current Accounts code. 

```{r example, eval = FALSE}
FromQuandl::imf_search('account')
```

Next use `imf_from_quandl()` to download this data. 

```{r example1 }
library(FromQuandl)
ca <- imf_from_quandl(countries = 'g7', indicators = 'BCA_NGDPD', start_date = '2008-01-01')
ca
```

The result is a `tibble` that it's ready to be used in `ggplot2`.

```{r example2} 
library(ggplot2)
library(ggthemes)

ca %>%
  ggplot(aes(date, value, color = country)) + 
  geom_line(size = 1, show.legend = FALSE) + 
  geom_hline(aes(yintercept = 0), color = 'red', linetype = 'dashed', alpha = 0.3) + 
  facet_wrap(~country, scale = "free_y") + 
  labs(title    = "Current Account Balance (% of GDP)",
       subtitle = "G7 Countries From 2005-01-01 through 2018-09-10",
       caption  = "Source: International Monetary Found (IMF).") + 
  theme_fivethirtyeight() + 
  scale_color_gdocs()

```
