---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```


# FromQuandl

[![Waffle.io - Columns and their card count](https://badge.waffle.io/Reckziegel/FromQuandl.svg?columns=all)](https://waffle.io/Reckziegel/FromQuandl) 

The goal of FromQuandl is to easy the search, download and data preprocessing steps that often happen when using the `Quandl` package in R.

Currently supports functions for IMF and World Bank datasets.


## Installation

You can install FromQuandl from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Reckziegel/FromQuandl")
```


## Examples

Suppose you would like to download the Current Account Balance (as % of GDP) for all countries of a specific region or with similar economic characteristics, like the G7. Use the `imf_search()` function to discover the Current Account code in `Quandl`. 

```{r example0}
library(FromQuandl)
fq_imf_search('account')
```

Next use `fq_imf()` to download and plot the data. 

```{r example1}
library(FromQuandl)
library(ggplot2)
library(dplyr)
library(ggthemes)

ca <- fq_imf(countries = 'g7', indicators = 'BCA_NGDPD', start_date = '2005-01-01')
ca

ca %>%
  ggplot(aes(x = date, y = value, color = country)) + 
  geom_line(size = 1, show.legend = FALSE) + 
  geom_hline(aes(yintercept = 0), color = 'red', linetype = 'dashed', alpha = 0.3) + 
  facet_wrap(~country, scale = "free_y") +
  labs(title    = "Current Account Balance (% of GDP)",
       subtitle = "G7 Countries From 2005-01-01 through 2018-09-10",
       caption  = "Source: International Monetary Found (IMF).") +
  theme_fivethirtyeight() +
  scale_color_gdocs()

```
 
The result is a `tibble` that it's ready to be used in `ggplot2`. 

There is no need to restrict the download to only one indicator. The `indicators` argument supports lists and vectors of strings as well, but be aware that may be safe using `Quandl.api_key()` if you want to access several time series at once.   

As a second example imagine that you want to downalod the rate of change in poverty statistics from the World Bank for all countries in the Commonwealth of Independent States. Simply run

```{r example2}
#library(FromQuandl)

# get poverty codes
poverty_data <- fq_wb_search('poverty')

# download data
fq_wb(countries = 'cis', indicators = poverty_data$code, transform = 'rdiff') 

```

The data is tidy and ready to be used with the `%>%` operatior.   

Additional information about the `fq_imf()`and `fq_wb()` can be found at the package documenation.

## Future Developments

This is a work in progress. Very soon the package will have a function to download the components of the most important stock indexes in US. Suggestions are welcome, :-).
